Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
figure text

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
    geom_jitter(width = .25) +
    geom_smooth(size=1) +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
    labs(y = "Prop. detected", x = element_blank()) +
    theme_few() + 
    theme(legend.position="none") +
    facet_grid(~detectorType) 
```
```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion face detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant."}

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture."}

>>>>

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
    geom_jitter(width = .25) +
    geom_smooth(size=1) +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
    labs(y = "Prop. detected", x = element_blank()) +
    theme_few() + 
    theme(legend.position="none") +
    facet_grid(~detectorType) 
```
```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion face and wrist/hand detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant."}

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face and wrist/hand detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture."}
